---
title: "Examples for miscr"
author: "Erik Loualiche"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
vignette: >
  %\VignetteIndexEntry{Examples for miscr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## `ls_objects`

Let's create a few objects in R but before we want to load some libraries:
```{r, results='hide', warning = F, error = F, message = F}
library(miscr)
library(data.table)
library(magrittr)
library(ggplot2)
```

```{r, results='asis'}
data(mtcars)
data(iris)
mtcars <- data.table(mtcars)
x <- 1
y <- c(0,1)
```

The results vary depending on options:
```{r}
ls_objects()
ls_objects(database = F)
```

## `datem_conv`

Easy to juggle with Ken French type of date format, yyymm and monthly specific date format for panel from statar yyyy'm'mm and vice versa. It is easy to see an example
```{r}
x <- 198312
y <- datem_conv(x)
z <- datem_conv(y)
print(y)
print(z)
```


## `fred_download`: clean dataset from Fred

To download data from FRED, use the fredr library and put the data in a decent format.
```{r, warning = F, message = F}
dt_gdp <- getFred("GDP")
dt_gdp
```


## `gg_bw`: mostly black & white theme

```{r, fig.width=6.8, fig.height=2.55}
p <- dt_gdp %>% 
  ggplot( aes(date, GDP) ) + geom_line()
p 
p + gg_bw()
```

## `dualplot`: two time series with different axes
```{r, fig.width=6.8, fig.height=2.55}
dt_gdp <- getFred("GDP")
dt_sp <- getFred("SP500")
dt_plot <- merge(dt_gdp[, GDP := log(GDP)], 
                 dt_sp[, .(SP500 = log(SP500), date_daily = date, date_ym)], by = c("date_ym"))
miscr:::dualplot(dt_plot$date_daily, dt_plot$GDP, dt_plot$SP500, x2 = dt_plot$date_daily,
                 ylim1 = c(9, 10), ylim2 = c(6, 8), ylab1 = c("gdp"), ylab2 = c("sp500"))
```

## `emailme`: email results to self

```{r, eval = F, results = 'hide'}
emailme(dt_gdp)      # email data
emailme(p + gg_bw()) # email plot
emailme()            # email last result
```

